\documentclass{letter}

\begin{document}
\address{2600 Bryant Street, Apt 2 \\ San Francisco CA 94110 \\ ilya.yakubovich@gmail.com \\ http://yak.nu}

\signature{Ilya Yakubovich}

\telephone{(415) 690 7342}

\makeatletter
\let\@texttop\relax
\makeatother

\begin{letter}{Dear Sir or Madam,}


I'd like to apply for the Senior User Interface Designer position at Atlassian. I'm a Human/Computer Interaction designer with a computer science background and over 6 years of experience in development, product management, and UX design.

Previously, I was the lead designer on the founding team of Yammer.com, an enterprise social network that's currently used at over 100,000 companies worldwide.

Early on, I was in charge of product management, visual design, user experience / interaction design, and some of the implementation (HTML/CSS). As the team expanded, I came to specialize in user experience, leaving the coding to dedicated front-end engineers.

Back then, Yammer was a small company, and as the only product manager I was responsible for setting up and administering our JIRA ticketing system. We all agreed that JIRA was the only tool flexible enough to represent real-life development processes, but constantly ran into usability problems. 

I think that Atlassian builds great products, but should consider investing more in design, and usability testing.

Please view my portfolio for examples of work, and an outline of my design process.

\closing{Thank you,}
\end{letter}

\end{document}
